Computational methods in landscape ecology

### 2024-09-19 Manuscript.qmd
Adding abstract

This is a test!

>>>>

## Purpose of Review {.unnumbered}

Landscapes can be defined as mosaics of different land covers, habitats, ecosystems, or land-use systems. 
The link between spatial heterogeneity and ecological processes is the core concept in the research field of landscape ecology. 
Due to its cross-disciplinary nature, the increasing availability of data, and the complexity of landscape systems, advanced computational methods are essential.

## Recent findings {.unnumbered}

This review provides an overview of recent developments in computational methods that have advanced landscape ecology research. 
We focus on key topics such as spatial patterns, connectivity, simulations and modeling, landscape genetics, and spatial planning.

## Summary {.unnumbered}

The review highlights key innovations, challenges, and potential future directions in the field, emphasizing the role of computational methods in addressing complex ecological questions.
